\objfield{READWRITE}{tau\_nmda}{0}{1000}{sec}{The time constant for NMDA channels.}
\objfield{READWRITE}{tau\_ampa}{0}{1000}{sec}{The time constant for AMPA channels.}
\objfield{READWRITE}{tau\_gaba\_a}{0}{1000}{sec}{The time constant for GABA\_A channels.}
\objfield{READWRITE}{tau\_gaba\_b}{0}{1000}{sec}{The time constant for GABA\_B channels.}
\objfield{READWRITE}{E\_nmda}{-1e30}{1e30}{V}{The reversal potential for NMDA channels.}
\objfield{READWRITE}{E\_ampa}{-1e30}{1e30}{V}{The reversal potential for AMPA channels.}
\objfield{READWRITE}{E\_gaba\_a}{-1e30}{1e30}{V}{The reversal potential for GABA\_A channels.}
\objfield{READWRITE}{E\_gaba\_b}{-1e30}{1e30}{V}{The reversal potential for GABA\_B channels.}
\objfield{READWRITE}{Mg\_conc}{-1e30}{1e30}{mMol}{Mg-concentration for voltage-dependence of NMDA-channel in}
\objfield{READWRITE}{Cm}{0}{1}{F}{The membrane capacity $C_m$}
\objfield{READWRITE}{Rm}{0}{1e30}{Ohm}{The membrane resistance $R_m$}
\objfield{READWRITE}{Vthresh}{-10}{100}{V}{If $V_m$ exceeds $V_{thresh}$ a spike is emmited.}
\objfield{READWRITE}{Vresting}{-1}{1}{V}{The resting membrane voltage.}
\objfield{READWRITE}{Vreset}{-1}{1}{V}{The voltage to reset $V_m$ to after a spike.}
\objfield{READWRITE}{Vinit}{-1}{1}{V}{The initial condition for $V_m$ at time $t=0$.}
\objfield{READWRITE}{Trefract}{0}{1}{sec}{The length of the absolute refractory period.}
\objfield{READWRITE}{Inoise}{0}{1}{A}{The standard deviation of the noise to be added each integration time constant.}
\objfield{READWRITE}{Iinject}{-1}{1}{A}{A constant current to be injected into the LIF neuron.}
\objfieldnu{READWRITE}{type}{-1e30}{1e30}{}{Type (e.g. inhibitory or excitatory) of the neuron}
\objfieldnu{READONLY}{summationPoint\_nmda}{-1e30}{1e30}{}{At this point synaptic input from NMDA-channels is summed up.}
\objfieldnu{READONLY}{summationPoint\_ampa}{-1e30}{1e30}{}{At this point synaptic input from AMPA-channels is summed up.}
\objfieldnu{READONLY}{summationPoint\_gaba\_a}{-1e30}{1e30}{}{At this point synaptic input from GABA\_A-channels is summed up.}
\objfieldnu{READONLY}{summationPoint\_gaba\_b}{-1e30}{1e30}{}{At this point synaptic input from GABA\_B-channels is summed up.}
\objfieldnu{READONLY}{Isyn}{-1e30}{1e30}{}{synaptic input current}
\objfieldnu{READONLY}{nIncoming}{-1e30}{1e30}{}{Number of incoming synapses}
\objfieldnu{READONLY}{nOutgoing}{-1e30}{1e30}{}{Number of outgoing synapses}
\objfield{READONLY}{Vm}{-1e30}{1e30}{V}{The membrane voltage $V_m$}
